### 2022-05-04 Publish Paper/manuscript_main.tex
Update paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancer leading causes of death worldwide. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing
incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment. Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data. In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example. In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of the metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

The Input schema is described as follow:

@@

@@

\subsection{Soft-Attention}
Applying Soft-Attention layer in deep learning is not a new approach. Soft-Attention have been used in various application: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention has ability to ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describe the flow of Soft-Attention module:
\[
	f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in a grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generate by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{Diagram/SoftAttention}
	\caption{Soft-Attention Module}
	\label{fig:softattention}
\end{figure}
In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{Diagram/SoftAttentionBlock}
	\caption{Soft-Attention Module}
	\label{fig:softattentionblock}
\end{figure}

\subsection{Backbone Model Architecture}
\subsection{Output Schema}
\subsection{Model}

\section{Training}
\subsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_i)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return. \\
Since the dataset face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. The overall loss function is then become\cite{8943952}:
\[
	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N} W_c \times y^c_n \times \log(h_\theta(x_n, \theta, c))
\]
where $W_c$ is the weight of class $c$, $y^c_n$ is the expected output of class $c$ at training example $n$. Otherwise, $h_\theta$ is the model with weight $\theta$.
\subsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{img/Confusion-matrix}
		\caption{Confusion Matrix}\label{Fig:Data1}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{img/AUC}
		\caption{Area Under the Curve}\label{Fig:Data2}
	\end{minipage}
\end{figure}
In this paper, the model is evaluated by using the confusion matrix and related metrics. The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively. 
\[
	A = \begin{bmatrix}
		a_{11} & a_{12} & \dots & a_{1j} \\
		a_{21} & a_{22} & \dots & a_{2j} \\
		\vdots & \vdots	&  & \vdots\\
		a_{i1} & a_{i2} & \dots & a_{ij} 
	\end{bmatrix}
\]
The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
	FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
	TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
		TN_1 & TN_2 & \dots & TN_c
	\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
\section{Results}
All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. The performance of all model is presented in the figure below:
\section{Conclusion}
\cite{08332}
\clearpage
\pagebreak

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung() who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancer leading causes of death worldwide. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing
incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need of effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in generally algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis and Medical Treatment. Medical imaging, including ultrasound, computed tomography, and magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosed results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history medical data. In Medical Treatment, AI models are applied for building solution for a specific disease, medicine revolutionize is an example. In various studies, AI algorithms has provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of the metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

The Input schema is described as follow:\\

@@

\end{figure}\\
Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
\subsection{Soft-Attention}
Applying Soft-Attention layer in deep learning is not a new approach. Soft-Attention have been used in various application: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention has ability to ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describe the flow of Soft-Attention module:
\[
	f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]
In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in a grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, and d$ is the shape of tensor generate by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 
	\includegraphics[width=1\linewidth]{Diagram/SoftAttention}
	\caption{Soft-Attention Module}
	\label{fig:softattention}

@@

In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
	\includegraphics[width=0.5\linewidth]{Diagram/SoftAttentionBlock}
	\caption{Soft-Attention Module}
	\label{fig:softattentionblock}
\end{figure}\\

\subsection{Backbone Model Architecture}
In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both test by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\begin{center}
	\begin{tabular}{|c | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
\end{center}

\subsection{Model}
The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer. It is described in the figure below:

\section{Training}
\subsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return. \\
Since the dataset face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. The overall loss function is then become\cite{8943952}:
\[
	L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N} W_c \times y^c_n \times \log(h_\theta(x_n, c))
\]
where $W_c$ is the weight of class $c$, $y^c_n$ is the expected output of class $c$ at training example $n$. Otherwise, $h_\theta$ is the model with weight $\theta$.
\subsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{img/Confusion-matrix}
		\caption{Confusion Matrix}\label{Fig:Data1}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{img/AUC}
		\caption{Area Under the Curve}\label{Fig:Data2}
	\end{minipage}
\end{figure}
In this paper, the model is evaluated by using the confusion matrix and related metrics. The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively. 
\[
	A = \begin{bmatrix}
		a_{11} & a_{12} & \dots & a_{1j} \\
		a_{21} & a_{22} & \dots & a_{2j} \\
		\vdots & \vdots	&  & \vdots\\
		a_{i1} & a_{i2} & \dots & a_{ij} 
	\end{bmatrix}
\]
The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
	FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
	TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
		TN_1 & TN_2 & \dots & TN_c
	\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
\section{Results}
All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. The performance of all model is presented in the figure below:
\section{Conclusion}
\cite{08332}
\clearpage
\pagebreak
